\recipe{Meggyleves}
\ingred{
\begin{tabular}{l l}
4 cup & Water\\
1 cup & sugar\\
1& cinnemon stick\\
4 cup & sour cherries pitted\\
pinch&salt\\
2 tbls&water\\
1 tbls& corn starch\\
\sfrac{1}{4} cup & cream\\
\end{tabular}
}
%\img{20110118_shanghaiNoodles_004.jpg}
In a large saucepan, bring the 4 cups of water, sugar and cinnamon stick to a boil.
Reduce heat to medium-low and simmer, stirring to dissolve the sugar, for about 2-3 minutes.
Add the cherries and a pinch of salt and simmer for another 30-40 minutes. Remove the cinnamon stick.
Stir the cornstarch into the 2 tablespoons of water and then quickly whisk the slurry into the simmering cherries. Simmer for another 2-3 minutes to thicken the soup a little.
Pour the soup into a bowl place into the refrigerator until well chilled. 
Just before serving, stir in the cream.

Variations:

To use sour cream instead of sweet cream, eliminate the cornstarch slurry and stir 2 tablespoons of flour into 3/4 cup sour cream. Whisk a little of the simmering soup into the sour cream, then whisk the sour cream into the soup. Simmer for another 5 minutes and chill.

If you use canned sour cherries, reduce cooking time to 10-15 minutes.

Stir in 1/2 cup of chilled red wine (preferably Hungarian), rosé wine or dry sherry with the cream.

To add even more flavor, save the cherry pits. Wrap them in a towel and pound with a hammer to crack them. Tie them up in a piece of cheesecloth and simmer along with the cherries. Remove along with the cinnamon stick.

Try using strawberries instead of cherries. Adjust the sugar down a little.