\recipe{Quinoa Stuffed Peppers}
\ingred{
\begin{tabular}{l l}
\sfrac{3}{4} cup &quinoa\\
4 large  &red or yellow bell peppers\\
1 tbls&olive oil\\
1 &red onion, chopped\\
1 cup& mushrooms sliced\\
2 & garlic cloves chopped\\
\sfrac{1}{4} tsp & red pepper flakes\\
1 tbls& tomato paste\\
1 medium&zucchini sliced\\
1 (14oz) can& diced tomatoes (drained)\\
1 tsp&oregano\\
\sfrac{1}{4} tsp& salt\\
\sfrac{1}{4} tsp&pepper\\
2 cup&Marinara Sauce\\
\end{tabular}
}
%\img{20110108_ChipotleHummus_006.jpg}
In a small saucepan bring 1\sfrac{1}{2} cups water to boil. Place the quinoa in a strainer and rinse under cold running water until the water runs clear. Stir the quinoa into the boiling water, cover and simmer until the quinoa is tender and the water is absorbed, about 15 minutes. Let stand covered, for 5 minutes. Fluff with a fork and set aside. 

Meanwhile, use a sharp paring knive to cut out the core from the peppers. Put out any seeds and rinse peppers inside and out. Place them cut side down on a microwave safe plate. Microwave on high power until slightly softened, 3 to 4 minutes. Set aside to cool. 

In a large skillet, heat the olive out over medium heat. Add the onion, mushroom, garlic, and red pepper flakes. Continue to cook stirring occasionally, until the mushroom are golden brown, about 8 minutes. 

Stir in the tomato pase and cook for 1 minute. Stir in the zucchini, tomatoes, oregano, and slat and pepper and cook for about 2 minutes. Stir in the quinoa and remove pan from heat. 

Place the peppers cut side up in a medium roasting pan. Spoon the filling into the peppers and fill the pan with water. \sfrac{1}{2} inch deep. Bake until peppers are tender and the top of the filling is lightly browned and crunchy, about 30 minutes. 

Meanwhile, in a small saucepan, heat the marinara over low heat. When peppers are cooked, place one on each of four plates. Sppon the sauce alongside or on top and serve. 